Chronic imaging of cortical oxygen tension and blood flow after targeted vascular occlusion

### 2018-04-24 article.tex
Implemented Andy's edits

% ----------------------------------------------------------------------------------------
% BEGIN ABSTRACT
% ----------------------------------------------------------------------------------------
\begin{abstract}
We present a dual-modality imaging system combining laser speckle contrast imaging and phosphorescence lifetime quenching to simultaneously measure cortical blood flow and oxygen tension (\pO) in mice. Phosphorescence signal localization is achieved through the use of a digital micromirror device (DMD) that allows for selective excitation of arbitrary regions of interest. By targeting both excitation maxima of the oxygen-sensitive porphyrin Oxyphor PtG4, we are able to examine the effects of wavelength and penetration depth on phosphorescence lifetime. We demonstrate the ability to measure static differences in \pO\ between arteries and veins and large changes during an hyperoxic challenge. We dynamically monitor blood flow and \pO\ during DMD-targeted photothrombotic occlusion of an arteriole and highlight the presence of an ischemia-induced depolarization. Chronic tracking of the ischemic lesion over seven days revealed a rapid recovery, with the targeted vessel fully reperfusing and \pO\ returning to baseline values within five days. This system has broad applications for studying the acute and chronic pathophysiology of ischemic stroke and other vascular diseases of the brain.
\end{abstract}

@@

\subsection{Imaging Instrumentation}
A schematic of the imaging system is presented in Fig.~\ref{fig:system_schematic}a. Laser speckle contrast imaging (LSCI) of blood flow was performed using a 685 nm laser diode (50 mW, HL6750MG, Thorlabs) illuminating the craniotomy at an oblique angle. Selection of the near-infrared laser diode was limited by the excitation and emission spectra of the oxygen-sensitive phosphorescent probe that dictated dichroic beamsplitter cutoff wavelengths. The scattered laser light was relayed to a CMOS camera (acA1300-60gmNIR, 1280 x 1024 pixels, Basler AG) with 2x magnification and acquired using custom software at 60 frames-per-second with a 5 ms exposure time.

@@

Simultaneously, laser light patterned by the DMD was delivered to the craniotomy to selectively excite the oxygen-sensitive phosphorescent probe. Wavelength has been shown to significantly affect the penetration depth and sampled volume of measurements through surface vasculature \cite{Davis:2011wj}, so two different lasers at 445 nm (200 mW, AixiZ) and 637 nm (250 mW, HL6388MG, Thorlabs) were selected to target the Soret and Q band excitation maxima of the dye \cite{Esipova:2011hi}. Each laser was used independently to collect \pO\ measurements from identical regions of interest for comparison. The 445 nm laser was modulated using an acousto-optic modulator (23080-2-LTD, Neos Technologies) while the 637 nm laser was directly modulated via its driver (LDD400-1P, Wavelength Electronics). Both lasers were modulated to produce 20 $\mu$s pulses of light for time domain lifetime measurements with a 6\% duty cycle and 3 kHz repetition rate using an National Instruments FlexRIO FPGA (NI PXIe-7965R and NI 5781).

@@

In order to obtain a more comprehensive look at vascular oxygenation within the LSCI field of view, an array of 12x8 rectangular tiles was sequentially projected. The resulting \pO\ maps (Fig.~\ref{fig:static_oxygen}c, d) coarsely follow the visible surface vasculature. As expected, the large branching vein has lower \pO\ values compared to the descending arteriole approaching from the bottom or the surrounding parenchyma. 445 nm excitation again results in a wider range of \pO\ values (45 - 85 mmHg) compared to 637 nm excitation (81 - 85 mmHg).

>>>>

% ----------------------------------------------------------------------------------------
% BEGIN ABSTRACT
% ----------------------------------------------------------------------------------------
\begin{abstract}
We present a dual-modality imaging system combining laser speckle contrast imaging and phosphorescence lifetime quenching to simultaneously map cortical blood flow and oxygen tension (\pO) in mice. Phosphorescence signal localization is achieved through the use of a digital micromirror device (DMD) that allows for selective excitation of arbitrary regions of interest. By targeting both excitation maxima of the oxygen-sensitive porphyrin Oxyphor PtG4, we are able to examine the effects of excitation wavelength and penetration depth on phosphorescence lifetime. We demonstrate the ability to measure differences in \pO\ between arteries and veins and large changes during an hyperoxic challenge. We dynamically monitor blood flow and \pO\ during DMD-targeted photothrombotic occlusion of an arteriole and highlight the presence of an ischemia-induced depolarization. Chronic tracking of the ischemic lesion over seven days revealed a rapid recovery, with the targeted vessel fully reperfusing and \pO\ returning to baseline values within five days. This system has broad applications for studying the acute and chronic pathophysiology of ischemic stroke and other vascular diseases of the brain.
\end{abstract}

@@

\subsection{Imaging Instrumentation}
A schematic of the imaging system is presented in Fig.~\ref{fig:system_schematic}a. Laser speckle contrast imaging (LSCI) of blood flow was performed using a 685 nm laser diode (50 mW, HL6750MG, Thorlabs) illuminating the craniotomy at an oblique angle. Selection of the near-infrared laser diode wavelength was limited by the excitation and emission spectra of the oxygen-sensitive phosphorescent probe that dictated dichroic beamsplitter cutoff wavelengths. The scattered laser light was relayed to a CMOS camera (acA1300-60gmNIR, 1280 x 1024 pixels, Basler AG) with 2x magnification and acquired using custom software at 60 frames-per-second with a 5 ms exposure time.

@@

Simultaneously, laser light patterned by the DMD was delivered to the craniotomy to selectively excite the oxygen-sensitive phosphorescent probe. Wavelength has been shown to significantly affect the penetration depth and sampled volume of measurements through surface vasculature \cite{Davis:2011wj}, so two different lasers at 445 nm (200 mW, AixiZ) and 637 nm (250 mW, HL6388MG, Thorlabs) were selected to target the Soret and Q band excitation maxima of the dye \cite{Esipova:2011hi}. Each laser was used independently to collect \pO\ measurements from identical regions of interest for comparison. The 445 nm laser was gated using an acousto-optic modulator (23080-2-LTD, Neos Technologies) while the 637 nm laser was directly gated via its driver (LDD400-1P, Wavelength Electronics). Both lasers were gated to produce 20 $\mu$s pulses of light for time domain lifetime measurements with a 6\% duty cycle and 3 kHz repetition rate using an National Instruments FlexRIO FPGA (NI PXIe-7965R and NI 5781).

@@

In order to obtain a more comprehensive look at vascular oxygenation within the LSCI field of view, an array of 12x8 rectangular tiles was sequentially projected. The tiles were displayed at 10 Hz with 200 decays averaged per pattern for a total acquisition time of 9.6 seconds. The resulting \pO\ maps (Fig.~\ref{fig:static_oxygen}c, d) coarsely follow the visible surface vasculature. As expected, the large branching vein has lower \pO\ values compared to the descending arteriole approaching from the bottom or the surrounding parenchyma. 445 nm excitation again results in a wider range of \pO\ values (45 - 85 mmHg) compared to 637 nm excitation (81 - 85 mmHg).
